GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis

### 2023-09-30 figs/GSE158422_split.Rmd
fix outputs

lares <- lapply( seq(100,1000,100) ,splitanalyze_la)

lares

@@

alres <- lapply( seq(100,1000,100) ,splitanalyze_al)

alres

@@

  lares <- as.data.frame(do.call(rbind,lares))
  lares$p_comm <-lares$common / lares$total
  lares$p_disc <-lares$discordant / lares$total
  lares$p_uncom <-lares$uncommon / lares$total
  lares
}

@@

  alres <- as.data.frame(do.call(rbind,alres))
  alres$p_comm <-alres$common / alres$total
  alres$p_disc <-alres$discordant / alres$total
  alres$p_uncom <-alres$uncommon / alres$total
  alres
}

>>>>

lares <- lapply( seq(100,300,100) ,splitanalyze_la)

@@

alres <- lapply( seq(100,300,100) ,splitanalyze_al)

@@

  laout <- data.frame(total,common,discordant,uncommon)
  laout$p_comm <-laout$common / laout$total
  laout$p_disc <-laout$discordant / laout$total
  laout$p_uncom <-laout$uncommon / laout$total
  laout
}

laout <- do.call(rbind,lapply(lares,lacompare))

@@

  alout <- data.frame(total,common,discordant,uncommon)
  alout$p_comm <-alout$common / alout$total
  alout$p_disc <-alout$discordant / alout$total
  alout$p_uncom <-alout$uncommon / alout$total
  alout
}

alout <- do.call(rbind,lapply(alres,alcompare))
